---
title: "R Notebook"
output: html_notebook
---

# Challenge 1

**Read new_diamonds dataset and see compute time differences when specifying columns while using read.csv(). Do this analysis using profvis.**

### Solution
```{r}
library(profvis)
# newDiamonds=rbind(diamonds, diamonds,diamonds, diamonds)
# newDiamonds2 = newDiamonds %>% select(carat,cut, price)
# write.csv2(newDiamonds2,file="new_diamonds.csv",row.names=FALSE)

profvis({
new_diamonds = read.csv2("datasets/new_diamonds.csv")

new_diamonds2 = read.csv2("datasets/new_diamonds.csv", colClasses = c("numeric",
                                                 "character","numeric"))
})

```

# Challenge 2

Verify the differences in compute time when calculating means of the numeric values of `new_diamonds`.

- Subset the relevant columns `new_diamonds_num = new_diamonds = new_diamonds[,c(1,3)]`
- Use microbenchmark on `colMeans()` and  `apply`

### Solution
```{r}

library(microbenchmark)

diamonds_num = new_diamonds[,c(1,3)]

microbenchmark(
  base::colMeans(diamonds_num),
  apply(diamonds_num,2,mean)
)


```

# Challenge 3

**Verify the compute time differences between:**

2. Preallocating the memory and create a new vector with `newvector=1:1000`
1. Create the same vector by generating a loop that grows the vector size with `newvector=c(newvector,x)`

### Solution
```{r}

create_vector =function(n){
  vec = c()
  for(i in 1:n){
    vec=c(vec,i)
  }
}

microbenchmark(
  newvector = c(1:1000),
  newvector2 = create_vector(1000)
)
```


# Challenge 4

**What does the lapply2 function do? Check compute time difference between `lapply2` and `lapply2_c`.**
- To do this you could appley the function `sd` to `x=list(1:200,1:100,100:340,10:90000)`

### Solution

`lapply2` applies a function to each elelement of a list.
```{r eval=TRUE}
lapply2 <- function(x, f, ...) {
  out <- vector("list", length(x))
  for (i in seq_along(x)) {
    out[[i]] <- f(x[[i]], ...)
  }
  out
}

lapply2_c <- compiler::cmpfun(lapply2)

x=list(1:200,1:100,100:340,10:90000)
microbenchmark(
  lapply2(x,sd),
  lapply2_c(x,sd),
  lapply(x,sd)
)

```

# Challenge 5

Modify the `add` function to return multiplication for 3 integers and check compute time differences with standard R operator. Do you expect a difference?

Can you extend the function to multiplication of 3 number in general?

### Solution
```{r}
library(Rcpp)

cppFunction('int mult(int x, int y) {
  int prod = x * y;
  return prod;
}')


x=17635
y=10002

microbenchmark(
  a=x*y,
  b=mult(x,y)
)

```


# Challenge 6 (Advanced)

Sample 20 passengers from the titanic and calculate the mean_age. Do this 10000 times (in parallel).

Use the titanic DataSet: `titanic <- read.csv("https://goo.gl/4Gqsnz")`

- Does the code run faster if run in parallel?

*Tip: Remove NA's using `na.omit(titanic)`*

### Solution
```{r}

library(dplyr)
library(parallel)
titanic = read.csv("https://goo.gl/4Gqsnz")
titanic= na.omit(titanic)

sample_mean =function(i){
  mean_Age = titanic %>% 
    sample_n(20) %>% 
    summarise(mean_age=mean(Age)) %>% 
    pull(mean_age)
  return(mean_Age)
}

system.time(lapply(1:10000, sample_mean))

system.time(mclapply(1:10000, sample_mean))

```




